Sparse Function-space Representation \\ of Neural Networks

### 2023-05-11 paper/main.tex
started new related work section

\textbf{Neural network to GP} Our goal is to find a kernel from which to build a sparse Gaussian process model. If we had the following function parameterization $g_i(\vx) = \phi^\T(\vx)$ we would could simply convert from weight space to function space the prior under the prior distribution meaning $\kappa(\vx, \vx) = \delta^{-1} \phi(\vx) \phi(\vx)^\T$ see \citet{rasmussen2006gaussian} for details. We linearise the neural network function

>>>>

\textbf{Neural network to GP} Our goal is to find a kernel from which to build a sparse Gaussian process model. If we had the following function parameterization $g_i(\vx) = \phi^\T(\vx)$ we would could simply convert from weight space to function space the prior under the prior distribution meaning $\kappa(\vx, \vx) = \delta^{-1} \phi(\vx) \phi(\vx)^\T$ see \citep{rasmussen2006gaussian} for details. We use the jacobian of the function $f_\transitionParams(\mathbf{x}_{i})$ and set that to be $\phi(\vx)$.
